\vspace{-1em}Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box

### 2015-05-27 paper/paper 2/dc-2015.tex
introduction

There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints easily and concisely and which is able to meet all requirements raised by data practitioners.
%which can be used to express constraints and to validate RDF data, 
%(e.g. existential and universal quantification, cardinality restrictions, and exclusive or of properties)
%\section{Ideas}
%constraint design patterns:
% - ontology design pattern.org
% - DSP uses other design pattern
% - constraint elements are the same / 
% - constraint / constraint elements / constraint design patterns / constraint language
%dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
%min car more powerful than req. propery
Thus, the idea behind this paper is to satisfy all RDF validation requirements
by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
We lately published a technical report (serving as second appendix of this paper) in which we describe the vocabulary in detail \cite{BoschEckert2015-2} (Section \ref{sec:vocabulary}).
The constraint type \emph{minimum qualified cardinality restrictions} (\emph{R-75}) can be instantiated to ensure
that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
This constraint can either be represented generically by \emph{description logics (DL)} {\small\ms{(Publication $\sqsubseteq$ $\geq$1 author.Person)}} or specifically by multiple domain-specific constraint languages:

@@

\textit{ReSh:}
Publication a rs:ResourceShape ; rs:property [
    rs:name "author" ; rs:propertyDefinition author ;
    rs:valueShape Person ;
    rs:occurs rs:One-or-many ; ] .

\textit{DSP:}
[   a dsp:DescriptionTemplate ; 
    dsp:resourceClass Publication ; 
    dsp:statementTemplate [ a dsp:NonLiteralStatementTemplate ;
        dsp:minOccur 1 ; dsp:maxOccur "infinity" ; 
        dsp:property author ; 
        dsp:nonLiteralConstraint [ a dsp:NonLiteralConstraint ;
            dsp:valueClass Person ] ] ] .
\end{ex}

The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
For this reason, the appendix of this paper contains mappings to \emph{DL} to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.

As every \emph{publication} must have at least one \emph{author} which must be a \emph{person} 
and since the book \emph{The-Lord-Of-The-Rings} is a \emph{publication} {\small\ms{(rdf:type(The-Lord-Of-The-Rings, Publication)),}} 
the book must have at least one \emph{author} relationship to a \emph{person}.
The constraint is violated either (1) if
\emph{The-Lord-Of-The-Rings} does not have any \emph{author} relationship, 
or (2) if the book has an \emph{author} which is not a \emph{person}
{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)},} {\small\ms{rdf:type(Tolkien, Hobbit)),}} 
or (3) if the book has an \emph{author} whose class is unknown
{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)).}}
In contrast, the book is a valid \emph{publication}, if it is connected to a \emph{person} via the property \emph{author}
{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)).}}

As there is no standard way to formulate constraints, 
semantically equivalent \emph{minimum qualified cardinality restrictions} may be represented by multiple languages - each of them having different syntax and semantics.
This causes confusion,
weakens the common understanding between several parties about the meaning of particular constraints, and
raises the question on how to ensure high data quality. 
Therefore, when choosing a language, say \ms{$\alpha$}, to express a constraint of an arbitrary constraint type, 
it should be possible to transform the constraint into a semantically equivalent constraint expressed by another constraint language \ms{$\beta$} (see Section \ref{sec:transformations}). 
This is important in order to enhance the interoperability of constraint languages and to resolve misunderstandings and ambiguities in the communication of RDF data producers and consumers 
since automatically performed constraint transformations avoid the necessity to understand several languages.

@@

@@

%This paper aims to address two main \textbf{audiences}:
%(1) RDF data providers and consumers seeking how to ensure high data quality and thus for ways to enhance the interoperability and common understanding of constraints expressible by multiple constraint languages and  
%(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.
The main contributions of this paper are:
(1) We provide a basic terminology and classification system for RDF constraints (Section \ref{sec:vocabulary}).
(2) We developed a vocabulary to describe constraints of any RDF constraint type generically (Section \ref{sec:vocabulary}).
(3) We show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (Section \ref{sec:transformations}).
(4) We explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages (Section \ref{sec:validation}).
%(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)

@@

We identified four dimensions to classify sets of constraints which can be instantiated from constraint types.
For each constraint type, we evaluated \cite{BoschNolleAcarEckert2015} in with which set of constraints their instances of contained.
For each set of constraints, we state the rounded number of associated constraint types in brackets.
%\begin{itemize}
  %\item \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints}
	%\item \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints}
	%\item \emph{Context:} \emph{property constraints} vs. \emph{class constraints}
	%\item \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
%\end{itemize}
%(1) \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints},
%(2) \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints},
%(3) \emph{Context:} \emph{property constraints} vs. \emph{class constraints}, and
%(4) \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}.
\textbf{\emph{Universality}:}
Constraints are expressible either generically (\emph{generic constraints}) using the \emph{RDF-CV}   
or specifically (\emph{specific constraints}) by domain-specific constraint languages. 
\textbf{\emph{DL Expressivity}:}
The \emph{RDF-CV} allows to describe 
constraints which are \emph{expressible in DL} (70\%) and which are \emph{not expressible in DL} (30\%). 
In case a constraint type is \emph{expressible in DL}, we determined which \emph{DL} constructs are needed to express the constraint type.
In addition, we mapped constraints of each constraint type to \emph{generic constraints} conforming to the \emph{RDF-CV} \cite{BoschNolleAcarEckert2015}.
This way, we show that constraints of each constraint type are representable as \emph{generic constraints} and therefore can be described generically by means of the \emph{RDF-CV}.
\textbf{\emph{Complexity}:}
\emph{Simple constraints} (2/3) denotes the set of atomic constraints. 
%which can be instantiated from almost 2/3 of the constraint types.
\emph{Complex constraints} (1/4) is the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}.
%and which are instances of 1/4 of the constraint types.
In case \emph{complex constraints} are expressible in \emph{DL}, 
\emph{DL} statements representing \emph{complex constraints} contain \emph{DL} statements standing for atomic and/or composed constraints. 
Nearly 15\% of the \emph{complex constraints}, however, can be formulated as \emph{simple constraints} when using them in terms of syntactic sugar. 
\textbf{\emph{Context}:}
\emph{Simple constraints} are applied on properties (\emph{property constraints}, 2/3),
on classes (\emph{class constraints}, 1/5), or
on properties and classes (\emph{property and class constraints}, 1/10).
%2/3 of all constraint types are types of \emph{property constraints}, 
%1/5 of \emph{class constraints}, and 
%approx. 10\% of \emph{property and class constraints}.
\emph{Simple constraints} must hold for individuals of their \emph{context classes}.
As \emph{context classes} of \emph{simple constraints} are reused within \emph{complex constraints},
it does not make sense to have terms standing for \emph{simple} and \emph{complex constraints} within the \emph{RDF-CV}. 
As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to generically describe constraints of all constraint types.
%\tb{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}
Altogether, instances of the most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}. 
%Thus, the majority of constraint types are directly and relatively easy formulated in form of \emph{simple constraints} which can be mapped to equivalent \emph{DL} constructs.

@@

\emph{Complex constraints} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
\emph{Exclusive or} is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
The \emph{complex constraint} \emph{context-specific exclusive or of property groups} (\emph{R-13})
restricts individuals of given classes to have properties of only one of multiple mutually exclusive property groups.
\emph{Publications} are either identified by an \emph{ISBN} and a \emph{title} (for books) or by an \emph{ISSN} and a \emph{title} (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}, which can be expressed in \emph{ShEx} as follows:

@@

\begin{ex}
Publication { 
    ( isbn string , title string ) |
    ( issn string , title string ) }
\end{ex}

@@

As the \emph{The-Great-Gatsby} is a \emph{publication} {\small\ms{(rdf:type(The-Great-Gatsby, Publication))}} having an \emph{ISBN} number {\small\ms{(isbn(The-Great-Gatsby, '978-0241965672'))}} and a \emph{title} {\small\ms{(title(The-Great-Gatsby, 'The Great Gatsby'))}} and not an additional \emph{ISSN} identifier, the \emph{The-Great-Gatsby} is a valid \emph{publication}.
%\begin{DL}
%rdf:type(BElannaTorres,Half-Klingon) \\
%klingonMother(BElannaTorres,Miral) \\
%klingonMother(BElannaTorres,JohnTorres)
%\end{DL}
The \emph{complex constraint} is mapped to the \emph{RDF-CV} (see Table \ref{tab:complex-constraints}) and expressed in \emph{DL} as follows:

@@

\begin{DL}
Publication $\sqsubseteq$ ($\neg$E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$F) \\ 
E $\equiv$ A $\sqcap$ B \\
F $\equiv$ C $\sqcap$ D \\
A $\sqsubseteq$ $\geq$ 1 isbn.string $\sqcap$ $\leq$ 1 isbn.string \\
B $\sqsubseteq$ $\geq$ 1 title.string $\sqcap$ $\leq$ 1 title.string \\
C $\sqsubseteq$ $\geq$ 1 issn.string $\sqcap$ $\leq$ 1 issn.string \\
D $\sqsubseteq$ $\geq$ 1 title.string $\sqcap$ $\leq$ 1 title.string \\
\end{DL}

@@

\begin{table}[H]
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Complex Constraints}
	\label{tab:complex-constraints}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
class & Publication & - & - & $\neg$E $\sqcap$ F, E $\sqcap$ $\neg$F & $\sqcup$ & - \\
class & $\neg$E $\sqcap$ F & - & - & $\neg$E, F & $\sqcap$ & - \\
class & E $\sqcap$ $\neg$F & - & - & E, $\neg$F & $\sqcap$ & - \\
class & $\neg$E & - & - & E & $\neg$ & - \\
class & E & - & - & A, B & $\sqcap$ & - \\
class & $\neg$F & - & - & F & $\neg$ & - \\
class & F & - & - & C, D & $\sqcap$ & - \\
class & A & - & - & A1, A2 & $\sqcap$ & - \\
property & A1 & isbn & - & string & $\geq$ & 1 \\
property & A2 & isbn & - & string & $\leq$ & 1 \\
class & B & - & - & B1, B2 & $\sqcap$ & - \\
property & B1 & title & - & string & $\geq$ & 1 \\
property & B2 & title & - & string & $\leq$ & 1 \\
class & C & - & - & C1, C2 & $\sqcap$ & - \\
property & C1 & issn & - & string & $\geq$ & 1 \\
property & C2 & issn & - & string & $\leq$ & 1 \\
class & D & - & - & D1, D2 & $\sqcap$ & - \\
property & D1 & title & - & string & $\geq$ & 1 \\
property & D2 & title & - & string & $\leq$ & 1 \\
		\end{tabular}
\end{table}

%Even though, tools may generate \emph{generic constraints} automatically, this 
\emph{Complex constraints} are composed of many other \emph{complex} (e.g. \emph{minimum and maximum qualified cardinality restrictions}) and \emph{simple constraints} (e.g. constraints on sets).
As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR)} are frequently used \emph{complex constraints},
we propose using them as \emph{simple constraints} - in terms of syntactic sugar.
As a consequence, the \emph{context-specific exclusive or of property groups} constraint above is represented as a \emph{generic constraint} more intuitively and concisely (see Table \ref{tab:simplified-complex-constraints}).

@@

\emph{Keys}, however, are even more general, i.e., a generalization of \emph{inverse functional properties} \cite{Schneider2009}.
A key can be a datatype, an object property, or a chain of properties.
For these generalization purposes, as there are different sorts of keys, and as keys can lead to undecidability, 
\emph{DL} is extended with \emph{key boxes} and a special construct \emph{keyfor} \cite{Lutz2005}.
When using the \emph{keyfor} \emph{DL} construct (\ms{isbn keyfor Book}), the \emph{complex constraint} can be expressed by only one \emph{simple property constraint} (see Table \ref{tab:primary-key-properties-as-simple-constraints} for the mapping to the \emph{RDF-CV}).

@@

\begin{table}[H]
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Primary Key Properties as Simple Constraints}
	\label{tab:primary-key-properties-as-simple-constraints}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
property & Book & isbn & - & - & keyfor & - \\
		\end{tabular}
\end{table}

>>>>

There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints easily and concisely and which is able to meet all requirements raised by data practitioners.
%which can be used to express constraints and to validate RDF data, 
%(e.g. existential and universal quantification, cardinality restrictions, and exclusive or of properties)
%\section{Ideas}
%constraint design patterns:
% - ontology design pattern.org
% - DSP uses other design pattern
% - constraint elements are the same / 
% - constraint / constraint elements / constraint design patterns / constraint language
%dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
%min car more powerful than req. propery
Thus, the idea behind this paper is to satisfy all RDF validation requirements
by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
We lately published a technical report (serving as second appendix of this paper) in which we describe the vocabulary in detail \cite{BoschEckert2015-2} (Section \ref{sec:vocabulary}).
The constraint type \emph{minimum qualified cardinality restrictions} (\emph{R-75}) can be instantiated to ensure
that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
This constraint can either be represented generically (\emph{generic constraints}) by \emph{description logics (DL)} {\small\ms{(Publication $\sqsubseteq$ $\geq$1 author.Person)}} or specifically (\emph{specific constraints}) by multiple domain-specific constraint languages:

@@

\textit{ReSh:} Publication a rs:ResourceShape ; rs:property [
          rs:propertyDefinition author ;
          rs:valueShape Person ;
          rs:occurs rs:One-or-many ; ] .

\textit{DSP:} [ dsp:resourceClass Publication ; dsp:statementTemplate [ 
          dsp:minOccur 1 ; dsp:maxOccur "infinity" ; 
          dsp:property author ; 
          dsp:nonLiteralConstraint [ dsp:valueClass Person ] ] ] .

\textit{SPIN:} CONSTRUCT \{ [ a spin:ConstraintViolation ... . ] \} WHERE \{ 
          ?this ?p ?o ; a ?C .
          BIND ( \textit{qualifiedCardinality}( ?this, ?p, ?C ) AS ?c ) .
          BIND( STRDT ( STR ( ?c ), xsd:nonNegativeInteger ) AS ?cardinality ) .
          FILTER ( ?cardinality < ?minimumCardinality ) . \}

\textit{SPIN function qualifiedCardinality:}										
SELECT ( COUNT ( ?arg1 ) AS ?c ) WHERE \{ ?arg1 ?arg2 ?o . ?o a ?arg3 . \}
\end{ex}

The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
For this reason, the appendix of this paper contains mappings to \emph{DL} to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
As every \emph{publication} must have at least one \emph{author} which must be a \emph{person} 
and since the book \emph{The-Lord-Of-The-Rings} is a \emph{publication}, 
%{\small\ms{(rdf:type(The-Lord-Of-The-Rings, Publication)),}} 
it must have at least one \emph{author} relationship to a \emph{person}.
The constraint is violated either (1) if
the book does not have any \emph{author} relationship, 
or (2) if it has an \emph{author} which is not a \emph{person},
%{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)},} {\small\ms{rdf:type(Tolkien, Hobbit)),}} 
or (3) if it has an \emph{author} whose class is unknown.
%{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)).}}
In contrast, the book is a valid \emph{publication}, if it is connected to a \emph{person} via the property \emph{author}.
%{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)).}}

The main contributions of this paper are:
(1) We provide a basic terminology and classification system for RDF constraints (Section \ref{sec:vocabulary}).
(2) As current high-level constraint languages do not support all constraint types, 
we developed a vocabulary to describe constraints of any RDF constraint type generically (Section \ref{sec:vocabulary}).
(3) We show how to enhance the interoperability of constraints expressed by different constraint languages by using the proposed vocabulary as an intermediate generic representation which enables transformations between semantically equivalent constraints of the same constraint type (Section \ref{sec:transformations}).
(4) We explain how arbitrary constraint languages may reuse validation implementations which are provided once for each constraint type (Section \ref{sec:validation}).

\subsection{How to Improve the Interoperability of RDF Constraints}
\label{sec:transformations}

RDF data providers have to ensure high data quality and therefore 
that their data conforms to constraints which may be part of contracts between data providers and consumers.
As there is no standard way to formulate constraints, 
semantically equivalent \emph{specific constraints}, so the \emph{minimum qualified cardinality restriction}, may be represented by a variety of languages - each of them having different syntax and semantics.
This causes confusion and weakens the common understanding between several parties about the meaning of particular constraints.
We propose transformations between semantically equivalent \emph{specific constraints}
(1) to avoid the necessity to understand several languages,
(2) to resolve misunderstandings in the communication of RDF data producers and consumers, and
(3) to enhance the interoperability of constraint languages.

We suggest to transform a \emph{specific constraint} (\emph{$sc_{\alpha}$}) of any constraint type expressed by language \emph{$\alpha$} into a semantically equivalent \emph{specific constraint} (\emph{$sc_{\beta}$}) of the same constraint type represented by any other language \emph{$\beta$}
by using the developed vocabulary to intermediately represent constraints in a generic way. 
%to enable these transformations.
By defining mappings between equivalent \emph{specific constraints} and the corresponding \emph{generic constraint} (\emph{gc}) we are able to convert them automatically: 
{\small\ms{$ gc = m_1(sc_{\alpha}) = m_2(sc_{\beta}) $}}.
Thereby, we do not need to define mappings between each pair of semantically equivalent \emph{specific constraints}.
Let's assume we are able to express constraints of the \emph{minimum qualified cardinality restrictions} constraint type by 10 languages.
Without an intermediate generic representation, we would have to define for each constraint type one mapping between each pair of \emph{specific constraints} expressed by \emph{n} languages
- that are \emph{\( {n \choose 2} \)} mappings (\emph{\( {10 \choose 2} \)} = 45 mappings).
With an intermediate generic representation, on the other side, we only need to define for each constraint type \emph{n} mappings 
%(1 mapping for each \emph{specific constraint}) 
from \emph{n} \emph{specific constraints} to the corresponding \emph{generic constraint} (10 mappings).
%Let's assume we are able to express a particular constraint type by 5/6/7/8/9/10 constraint languages.
%Without the intermediate \emph{generic constraint}, we would have to define for each constraint type \emph{1} mapping for each pair of \emph{specific constraints} (expressed by different constraint languages)
%that are \emph{\( {n \choose 2} \)} mappings (10/15/21/28/36/45 mappings).
%With an intermediate \emph{generic constraint}, however, we only need to define for each constraint type \emph{n} mappings (1 mapping for each \emph{specific constraint}) from \emph{n} \emph{specific constraints} to the corresponding \emph{generic constraint} (5/6/7/8/9/10 mappings).
For the \emph{minimum qualified cardinality restriction}, one mapping (\emph{$m_1(sc_{OWL 2})$}, \emph{$m_2(sc_{ShEx})$}, \emph{$m_3(sc_{ReSh})$}, \emph{$m_4(sc_{DSP})$},...) is defined for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ShEx}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{DSP}$},...) to the corresponding \emph{generic constraint} (\emph{gc}).

\subsection{How to Provide the Validation of RDF Constraints Out-Of-The-Box}
\label{sec:validation}

@@

SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints, although, it is not ideal for their formulation. 
In contrast, OWL 2, DSP, ReSh, and ShEx constraints are comparatively easy to understand. 
We use SPIN as basis to define a
validation environment\footnote{Online demo available at \url{http://purl.org/net/rdfval-demo}, source code available at: \url{https://github.com/boschthomas/rdf-validator}\label{rdf-validator}} in which the validation of any constraint language can be implemented by representing them in SPARQL.
The only limitation is that constraint languages must be represented in RDF.
The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations \cite{BoschEckert2014-2}.
This way, we are able to offer RDF data validation according to all \emph{specific constraints} (expressed by any constraint language) by defining mappings from each \emph{specific constraint} to \emph{SPIN}. 
We already specified mappings to \emph{SPIN} for all \emph{OWL 2} and \emph{DSP}\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} constructs and for some \emph{ReSh} and \emph{ShEx} constructs.
As constraint languages differ in syntax and semantics it is rather difficult to ensure that semantically equivalent \emph{specific constraints} always lead to identical validation results.

@@

%This paper aims to address two main \textbf{audiences}:
%(1) RDF data providers and consumers seeking how to ensure high data quality and thus for ways to enhance the interoperability and common understanding of constraints expressible by multiple constraint languages and  
%(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.

%(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)

@@

We identified four dimensions to classify sets of constraints which can be instantiated from constraint types.
For each constraint type, we evaluated \cite{BoschNolleAcarEckert2015} in with which set of constraints their instances of contained.
For each set of constraints, we state the rounded number of associated constraint types in brackets.
%\begin{itemize}
  %\item \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints}
	%\item \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints}
	%\item \emph{Context:} \emph{property constraints} vs. \emph{class constraints}
	%\item \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
%\end{itemize}
%(1) \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints},
%(2) \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints},
%(3) \emph{Context:} \emph{property constraints} vs. \emph{class constraints}, and
%(4) \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}.
\textbf{\emph{Universality}:}
Constraints are expressible either generically (\emph{generic constraints}) using the \emph{RDF-CV}   
or specifically (\emph{specific constraints}) by domain-specific constraint languages. 
\textbf{\emph{DL Expressivity}:}
The \emph{RDF-CV} allows to describe 
constraints which are \emph{expressible in DL} (70\%) and which are \emph{not expressible in DL} (30\%). 
In case a constraint type is \emph{expressible in DL}, we determined which \emph{DL} constructs are needed to express the constraint type.
In addition, we mapped constraints of each constraint type to \emph{generic constraints} conforming to the \emph{RDF-CV} \cite{BoschNolleAcarEckert2015}.
This way, we show that constraints of each constraint type are representable as \emph{generic constraints} and therefore can be described generically by means of the \emph{RDF-CV}.
\textbf{\emph{Complexity}:}
\emph{Simple constraints} (2/3) denotes the set of atomic constraints. 
%which can be instantiated from almost 2/3 of the constraint types.
\emph{Complex constraints} (1/4) is the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}.
%and which are instances of 1/4 of the constraint types.
In case \emph{complex constraints} are expressible in \emph{DL}, 
\emph{DL} statements representing \emph{complex constraints} contain \emph{DL} statements standing for atomic and/or composed constraints. 
The constraints of almost 15\% of the constraint types are \emph{complex constraints}
which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
\textbf{\emph{Context}:}
\emph{Simple constraints} are applied on properties (\emph{property constraints}, 2/3),
on classes (\emph{class constraints}, 1/5), or
on properties and classes (\emph{property and class constraints}, 1/10).
%2/3 of all constraint types are types of \emph{property constraints}, 
%1/5 of \emph{class constraints}, and 
%approx. 10\% of \emph{property and class constraints}.
\emph{Simple constraints} must hold for individuals of their \emph{context classes}.
As \emph{context classes} of \emph{simple constraints} are reused within \emph{complex constraints},
it does not make sense to have terms standing for \emph{simple} and \emph{complex constraints} within the \emph{RDF-CV}. 
As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to generically describe constraints of all constraint types.
%\tb{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}
Altogether, instances of the most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}. 
%Thus, the majority of constraint types are directly and relatively easy formulated in form of \emph{simple constraints} which can be mapped to equivalent \emph{DL} constructs.

@@

%\emph{Complex constraints} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
\emph{Context-specific exclusive or of property groups} (\emph{R-13}) \emph{complex constraints}
restrict individuals of given classes to have all properties of exactly one of multiple mutually exclusive property groups.
\emph{Publications}, e.g., are either identified by an \emph{ISBN} and a \emph{title} (for books) or by an \emph{ISSN} and a \emph{title} (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}. 
As the \emph{The-Great-Gatsby} is a \emph{publication} with an \emph{ISBN} and a \emph{title} without an \emph{ISSN}, 
\emph{The-Great-Gatsby} is considered as a valid \emph{publication}.
This \emph{complex constraint} is expressible specifically by \emph{ShEx} and generically by \emph{DL} (and can therefore be mapped to the \emph{RDF-CV} \cite{BoschEckert2015-2}):

@@

\begin{ex}[commandchars=\\\{\}]
\textit{ShEx:} Publication { ( isbn string , title string ) | ( issn string , title string ) }
\end{ex}

@@

%\begin{DL}
%rdf:type(BElannaTorres,Half-Klingon) \\
%klingonMother(BElannaTorres,Miral) \\
%klingonMother(BElannaTorres,JohnTorres)
%\end{DL}
%The \emph{complex constraint} is mapped to the \emph{RDF-CV} (see Table \ref{tab:complex-constraints}) and expressed in \emph{DL} as follows:

@@

\begin{DL}
\textbf{Publication $\sqsubseteq$ ($\neg$E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$F)} , E $\equiv$ A $\sqcap$ B , F $\equiv$ C $\sqcap$ D \\
A $\sqsubseteq$ $\geq$ 1 isbn.string $\sqcap$ $\leq$ 1 isbn.string , B $\sqsubseteq$ $\geq$ 1 title.string $\sqcap$ $\leq$ 1 title.string \\
C $\sqsubseteq$ $\geq$ 1 issn.string $\sqcap$ $\leq$ 1 issn.string , D $\sqsubseteq$ $\geq$ 1 title.string $\sqcap$ $\leq$ 1 title.string \\
\end{DL}

@@

%\begin{table}[H]
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\caption{Complex Constraints}
	%\label{tab:complex-constraints}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
%class & Publication & - & - & $\neg$E $\sqcap$ F, E $\sqcap$ $\neg$F & $\sqcup$ & - \\
%class & $\neg$E $\sqcap$ F & - & - & $\neg$E, F & $\sqcap$ & - \\
%class & E $\sqcap$ $\neg$F & - & - & E, $\neg$F & $\sqcap$ & - \\
%class & $\neg$E & - & - & E & $\neg$ & - \\
%class & E & - & - & A, B & $\sqcap$ & - \\
%class & $\neg$F & - & - & F & $\neg$ & - \\
%class & F & - & - & C, D & $\sqcap$ & - \\
%class & A & - & - & A1, A2 & $\sqcap$ & - \\
%property & A1 & isbn & - & string & $\geq$ & 1 \\
%property & A2 & isbn & - & string & $\leq$ & 1 \\
%class & B & - & - & B1, B2 & $\sqcap$ & - \\
%property & B1 & title & - & string & $\geq$ & 1 \\
%property & B2 & title & - & string & $\leq$ & 1 \\
%class & C & - & - & C1, C2 & $\sqcap$ & - \\
%property & C1 & issn & - & string & $\geq$ & 1 \\
%property & C2 & issn & - & string & $\leq$ & 1 \\
%class & D & - & - & D1, D2 & $\sqcap$ & - \\
%property & D1 & title & - & string & $\geq$ & 1 \\
%property & D2 & title & - & string & $\leq$ & 1 \\
		%\end{tabular}
%\end{table}

%Even though, tools may generate \emph{generic constraints} automatically, this 
The \emph{DL} statements demonstrate that the \emph{complex constraint} 
is composed of many other \emph{complex} (e.g. \emph{minimum and maximum qualified cardinality restrictions}) and \emph{simple constraints} (e.g. constraints on sets).
As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR)} are frequently used \emph{complex constraints},
we propose using them in terms of syntactic sugar as \emph{simple constraints}.
As a consequence, the \emph{context-specific exclusive or of property groups} \emph{complex constraint} is represented as a \emph{generic constraint} by means of the \emph{RDF-CV} more intuitively and concisely (Table \ref{tab:simplified-complex-constraints}).

@@

\emph{Keys}, however, are even more general, i.e., a generalization of \emph{inverse functional properties} \cite{Schneider2009}.
A key can be a datatype, an object property, or a chain of properties.
For these generalization purposes, as there are different sorts of keys, and as keys can lead to undecidability, 
\emph{DL} is extended with a special construct \emph{keyfor} \cite{Lutz2005}.
When using \emph{keyfor} (\ms{isbn keyfor Book}), 
the \emph{complex constraint} can be simplified as a \emph{simple constraint} which looks like the following in RDF turtle syntax:

@@

%\begin{table}[H]
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\caption{Primary Key Properties as Simple Constraints}
	%\label{tab:primary-key-properties-as-simple-constraints}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
%property & Book & isbn & - & - & keyfor & - \\
		%\end{tabular}
%\end{table}

\begin{ex}[commandchars=\\\{\}]
[   a \textit{rdfcv:PropertyConstraint} , \textit{rdfcv:SimpleConstraint} ;
    \textit{rdfcv:contextClass} Book ; \textit{rdfcv:leftProperties} ( isbn ) ; \textit{rdfcv:constrainingElement} "keyfor" ] .
\end{ex}
